Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_appendix.tex
appendix updated

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \texttt{WeightWatcher} tool (v0.2.7)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions.

@@

The reader may regenerat all of the  results of Section~\ref{sxn:all_cv_models} 
\texttt{WeightWatcher} results using the Google Colab Jupyter notebooks (in the \texttt{ww-colab} folder)
and  the \texttt{WeightWatcher} tool, 
and/or simply reproduce the Tables and Figures using the Jupyter notebooks (shown in Table~\ref{table:notebooks}),
and the pre-computed \texttt{WeightWatcher} datasets (in the \texttt{data/osmr} folder).
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.

@@

Table~\ref{table:results} and Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I} below present results for OLS 
(Ordinary Least Squares) regressions for every dataset and architecture series listed in Table~\ref{table:architectures},
 created by running the \texttt{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package}
on numerous pretrained models taken from the \texttt{OSMR/imgclsmob Sandbox} github repository of pretrained CV DNN model
ggithub repository. \michael{citation here ?}
In each Figure,  each row of subfigures, for a given pretrained model and dataset, depicts the average Norm-based and Power Law metrics
 ($\langle\log\Vert\cdot\Vert_{F}\rangle$,    $\langle\log\Vert\cdot\Vert_{\infty}\rangle$,
$\hat{\alpha}$,  $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$)
 against the Top1 Test Accuracy, as reported in the github repository README file~\cite{osmr} ).
, along with a shaded area
representing the $95\%$ confidence bound.
For each regression, we report the RMSE, R2 regresssion metrics, and Kendal-$\tau$ rank correlation metric,
both in the title of each subfiguire, and in Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}, respectively.
To reproduce these Figures and Tables, see the \texttt{OSMR-Analysis.ipynb} python Jupyter Notebook, as listed in Table~\ref{},
and provided github repo accompanying this paper.
The reader may regenerate these Figures and Tables,
along with more fine grained results, by rerunning
 the \texttt{OSMR-Analysis.ipynb} python Jupyter Notebook (see Table~\ref{table:notebooks}), which 
analyzes the data in the \texttt{df\_all.xlsx} file. 
This repository also contains the original \texttt{Google Colab} notebooks, run in January 2020, 
which downloads the pretrained models and  and runs the \texttt{WeightWatcher} tool on them.
%To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 rrors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
%We record the $RMSE$, $R^{2}$, and Kendall-$\tau$ for each metric, averaged over all regressions for all architectures and datasets;
%see Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}, respectively.
%captions fixed in table Ktau.  
%In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The reader may also run the most current version of  \texttt{WeightWatcher} (ww0.4.1) on individual 
pretrained models (which may also have changed slightly since January 2020), 
such as the ResNet models, trained on the ImageNet-1K dataset, using the \texttt{WeightWatcher-ResNet-1K.ipynb} notebook.
The final analysis includes 108 regressions in all.%, those with 4 or more models.%, with a positive $R^2$.

See
Figure~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I} for more details.
%5Figure~\ref{fig:summary_regressions_B},
%Figure~\ref{fig:summary_regressions_C},
%Figure~\ref{fig:summary_regressions_D},
%Figure~\ref{fig:summary_regressions_E},
%Figure~\ref{fig:summary_regressions_F},
%Figure~\ref{fig:summary_regressions_G},
%Figure~\ref{fig:summary_regressions_H}, and

\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}
\charles{below}
From these Figures, we recognize fits of varying quality, ranging from remarkably good to completely uncorrelated.
Starting with the best, consider the Imagenet-1K PreResNet results.  Figure~\ref{fig:summary_regressions_A_10} shows 
the Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$, 
which has a rather large $RMSE=3.93$, and rather small $R2=0.36$, and Kendal-$\tau=0.54$, and
has 6 out of 13 points outside the $95\%$ confidence bands.  In contrast, 
the Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$, 
in  Figure~\ref{fig:summary_regressions_A_12} , 
has a much smaller $RMSE=1.93$, and much larger  $R2=0.85$, and Kendal-$\tau=0.87$, 
and only 2 points outside the $95\%$ confidence bands.
For examples of lower quality fits, consider the SqueezeNext results, as shown Figures~\ref{fig:summary_regressions_C_10} and 
~\ref{fig:summary_regressions_C_12}.  
The Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$,
is visually anti-correlated  with the test accuracies
(as it is with ShuffleNet, in Figure ~\ref{fig:summary_regressions_B_02}).
with a very large $95\%$ confidence band, with only 2 points close to the regression line,
a large RMSE,  $R2=0.07$ (i.e zero), and small Kendal-$\tau=0.33$.
The Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$ is (as always) positively-correlated
with test accuracies, but with $R2=43$, which is not great--but not zero, and a reasonable Kendal-$\tau=0.73$.

>>>>

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \texttt{WeightWatcher} tool)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions.

@@

The reader may regenerate all of the  results of Section~\ref{sxn:all_cv_models} 
\texttt{WeightWatcher} results using the Google Colab Jupyter notebooks (in the \texttt{ww-colab} folder)
and  the \texttt{WeightWatcher} tool, 
and/or simply reproduce 
Table~\ref{table:results}, as well as Tables~\ref{table:RMSEresults}-\ref{table:Ktauresults}
and  Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I},
using the Jupyter notebooks (shown in Table~\ref{table:notebooks}),
and the pre-computed \texttt{WeightWatcher} datasets (in the \texttt{data/osmr} folder).
The pretrained models, trained on ImageNet-1K and the other datasets, 
are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]},
and \texttt{WeightWatcher} version ww0.2.7.  Results can be recomputed using the current version (ww0.4.1)
using the \texttt{ww2x=True} back compatability option, although note the pretrained models must
be downloaded and  may have changed slightly.
The data files currently provided are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in 
Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}
and Tables

@@

Table~\ref{table:results} and Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I} below present results for OLS 
(Ordinary Least Squares) regressions for every dataset and architecture series listed in Table~\ref{table:architectures},
 created by running the \texttt{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package}
on numerous pretrained models taken from the \texttt{OSMR/imgclsmob Sandbox} github repository of pretrained CV DNN model
ggithub repository. \michael{citation here ?}
In each Figure,  each row of subfigures, for a given pretrained model and dataset, depicts the average Norm-based and Power Law metrics
 ($\langle\log\Vert\cdot\Vert_{F}\rangle$,    $\langle\log\Vert\cdot\Vert_{\infty}\rangle$,
$\hat{\alpha}$,  $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$)
 against the Top1 Test Accuracy, as reported in the github repository README file~\cite{osmr} ),
along with a shaded area representing the $95\%$ confidence bound.
For each regression, we report the RMSE, R2 regresssion metrics, and Kendal-$\tau$ rank correlation metric,
both in the title of each subfiguire, and in Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}, respectively.
To reproduce these Figures and Tables, see the \texttt{OSMR-Analysis.ipynb} python Jupyter Notebook, as listed in Table~\ref{},
and provided github repo accompanying this paper.
The reader may regenerate these Figures and Tables,
and even more fine grained results, by rerunning
 the \texttt{OSMR-Analysis.ipynb} python Jupyter Notebook (see Table~\ref{table:notebooks}), which 
analyzes the precomputed data in the \texttt{df\_all.xlsx} file. 
This repository also contains the original \texttt{Google Colab} notebooks, run in January 2020, 
which downloads the pretrained models and  and runs the \texttt{WeightWatcher} tool on them.
%To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 rrors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
%We record the $RMSE$, $R^{2}$, and Kendall-$\tau$ for each metric, averaged over all regressions for all architectures and datasets;
%see Table~\ref{table:RMSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:Ktauresults}, respectively.
%captions fixed in table Ktau.  
%In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The reader may also run the  \texttt{WeightWatcher} locally on each of the 
pretrained models,
such as the ResNet models, trained on the ImageNet-1K dataset, using the \texttt{WeightWatcher-ResNet-1K.ipynb} notebook.
(However, note that the models may have changed, giving slightly different results).
The final analysis includes 108 regressions in all.%, those with 4 or more models.%, with a positive $R^2$.
See Figure~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I} for more details.
%5Figure~\ref{fig:summary_regressions_B},
%Figure~\ref{fig:summary_regressions_C},
%Figure~\ref{fig:summary_regressions_D},
%Figure~\ref{fig:summary_regressions_E},
%Figure~\ref{fig:summary_regressions_F},
%Figure~\ref{fig:summary_regressions_G},
%Figure~\ref{fig:summary_regressions_H}, and

\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}
\charles{below}
From these Figures, we recognize fits of varying quality, ranging from remarkably good to completely uncorrelated.
Starting with the best, consider the Imagenet-1K PreResNet results.  Figure~\ref{fig:summary_regressions_A_10} shows 
the Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$, 
which has a rather large $RMSE=3.93$, and rather small $R2=0.36$, and Kendal-$\tau=0.54$, and
has 6 out of 13 points outside the $95\%$ confidence bands.  In contrast, 
the Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$, 
in  Figure~\ref{fig:summary_regressions_A_12} , 
has a much smaller $RMSE=1.93$, and much larger  $R2=0.85$, and Kendal-$\tau=0.87$, 
and only 2 points outside the $95\%$ confidence bands.
For examples of lower quality fits, consider the SqueezeNext results, as shown Figures~\ref{fig:summary_regressions_C_10} and 
~\ref{fig:summary_regressions_C_12}.  
The Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$ appears
visually anti-correlated with the test accuracies
(as it is with ShuffleNet, in Figure ~\ref{fig:summary_regressions_B_02}).
It has a very large $95\%$ confidence band, with only 2 points close to the regression line, 
a large RMSE,  $R2=0.07$ (i.e zero), and small Kendal-$\tau=0.33$.  
The Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$ is (as always) positively-correlated
with test accuracies, but with $R2=0.43$, show some linear correaltion, and a reasonable Kendal-$\tau=0.73$,
showing moderately strong rank correlation.
